Active Learning for SAT-Solver Benchmarking

### 2022-09-26 paper/paper.tex
Update github links

For reproducibility, our source code, all experiments, and data are available on GitHub\footnote{\url{https://github.com/mathefuchs/al-sat-benchmarking-experiments}}.

@@

\subsection{Implementation Details}
For reproducibility, our source code, all experiments, and data are available on GitHub\footnote{\url{https://github.com/mathefuchs/al-sat-benchmarking-experiments}}.
It is implemented in \textsc{Python} using \textit{scikit-learn}~\cite{scikit-learn} for making predictions and \textit{gbd-tools}~\cite{IserS18} for SAT-instance retrieval.

>>>>

For reproducibility, our source code, all experiments, and data are available on GitHub\footnote{\url{https://github.com/mathefuchs/al-for-sat-solver-benchmarking}}.

@@

\subsection{Implementation Details}
For reproducibility, our source code, all experiments, and data are available on GitHub\footnote{\url{https://github.com/mathefuchs/al-for-sat-solver-benchmarking}}.
It is implemented in \textsc{Python} using \textit{scikit-learn}~\cite{scikit-learn} for making predictions and \textit{gbd-tools}~\cite{IserS18} for SAT-instance retrieval.
